TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-11 paper/paper.tex
paper: changed sentence in sub:TCP_Congestion_Algorithms and added another ref

	\subsection{TCP Congestion Algorithms}
	The most common TCP congestion algorithms are CTCP, CUBIC and BIC. CTCP is the default congestion algorithm in Microsoft Windows Server 2008 and newer \cite{cubic-kernel-version}. CUBIC is the default congestion algorithm in Linux distributions with kernel versions 2.6.19 and higher \cite{cubic-kernel-version}. BIC was the default congestion algorithm in earlier Linux distributions from kernel version 2.6.8 until 2.6.19 \cite{bic-kernel-version} \cite{cubic-kernel-version}. DCTCP and BBR will also be tested as those protocols are newer. DCTCP is specifically designed for datacenters \cite{dctcp-congestion} and BBR is a new congestion protocol not yet widely deployed \cite{bbr-congestion}.

>>>>

	\subsection{TCP Congestion Algorithms}
	The most common TCP congestion algorithms are CTCP, CUBIC and BIC. CTCP is the default congestion algorithm in Microsoft Windows Server 2008 and newer \cite{cubic-kernel-version}. CUBIC is the default congestion algorithm in Linux distributions with kernel versions 2.6.19 and higher \cite{cubic-kernel-version}. BIC was the default congestion algorithm in earlier Linux distributions from kernel version 2.6.8 until 2.6.19 \cite{bic-kernel-version} \cite{cubic-kernel-version}. DCTCP and BBR will also be tested as those protocols are new and upcoming---they are included in Linux since 4.9 (December 2016) \cite{linux-bbr}. DCTCP is specifically designed for datacenters \cite{dctcp-congestion} and BBR is a new algorithm meant for general use \cite{bbr-congestion}.
